Consistency scores in text data

### 2020-08-05 outputs/documents/paper.Rmd
implementations on Word2Vec and GloVe

**(Ke-Li add brief write-up of implementation in R please.)**
There are a few packages for implementing a Word2Vec model in R. The packages are "rword2vec" by Mukul Chaware and "word2vec" by Jan Wijffels, BNOSAC, and Max Fomichev. Both packages uses the same algorithm that Word2Vec uses to produce word representations, but they do not have an affiliation with Google. Another way to implement a Word2Vec model in R is through Keras package. Keras is an API for deep learning written in Python (@chollet2015keras) and the Keras package provides an R interface to Keras **(Ke-Li add citation for the package)**. RStudio published a tutorial for implementing the skip-gram model of Word2Vec (@falbel2017word); we intend to follow this tutorial as the approach to implement a Word2Vec model.

@@

There are more than one way to implement GloVe word embedding model in R. One way is to load GloVe embeddings into a frozen Keras Embedding layer **(Keli add citation to the blog post by Keras)** using the Keras R package (**(Keli add citation to package)**). Another way, as mentioned and briefly demonstrated by Rstudio in their blog post, is to use the "text2vec" package developed by Dmitriy Selivanov **(Ke-Li add package citation)**.

@@

OpenAI has made GPT-2 open-sourced through Github with Python and Tensorflow. There is also a package in R that wraps the Python code into a R package, created by @keydanaluraschi2019gpt2. However, the R package only permits exploratory experiments with the pre-trained tasks; fine-tuning for new tasks is not available thorough R. In our project, we aim to use fine-tune GPT-2 to perform a text cleaning task **(Ke-Li add more about how we use fine-tuning to train GPT-2 for text cleaning, or try with other task if text cleaning is not achieved)**.

@@

>>>>

**(Ke-Li add brief write-up of implementation in R please.)**
There are a few packages for implementing a Word2Vec model in R. The packages are "rword2vec" by Mukul Chaware and "word2vec" by Jan Wijffels, BNOSAC, and Max Fomichev. Both packages uses the same algorithm that Word2Vec uses to produce word representations, but they do not have an affiliation with Google. Another way to implement a Word2Vec model in R is through Keras package. Keras is an API for deep learning written in Python (@chollet2015keras) and the Keras package provides an R interface to Keras **(Ke-Li add citation for the package)**. RStudio published a tutorial for implementing the skip-gram model of Word2Vec (@falbel2017word) through Keras. We intend to follow this tutorial as the approach to implement a Word2Vec model. Following the demonstration, functions are defined to mimic the skip-gram algorithm of Word2Vec. The embedding dimensions, the size of the context window and the number of samples are configurable. As a result, a embedding matrix is obtained and serves as the look-up table of the word vectors.

@@

There are more than one way to implement GloVe word embedding model in R. One way is to load GloVe embeddings into a frozen Keras Embedding layer **(Keli add citation to the blog post by Keras)** using the Keras R package (**(Keli add citation to package)**). Another way, as mentioned and briefly demonstrated by Rstudio in their blog post, is to use the "text2vec" package developed by Dmitriy Selivanov **(Ke-Li add package citation)**. Keras published a blog post on pre-trained word embeddings through GloVe in R. In this project, we intend to follow the blog post for implementing GloVe through the Keras R package **(Keli add citation to the blog post by Keras)**. The blog post is aimed to create a word embedding model for text classification. However, we will only use the guide create a embedding matrix and skip the steps of text classification. Similar to the Word2Vec embedding matrix, the GloVe embedding matrix is obtained and serves as a look-up table.

@@

OpenAI has made GPT-2 open-sourced through Github with Python and Tensorflow. There is also a package in R that wraps the Python code into a R package, created by @keydanaluraschi2019gpt2. However, the R package only permits exploratory experiments with the pre-trained tasks; fine-tuning for new tasks is not available thorough R. In our project, we aim to use fine-tune GPT-2 to perform a text cleaning task.

@@

**(Keli adds implementation of BERT in R)**
BERT implementation in R is also possible through Keras. Zhao HG (**Replace by citation**) created a python module called Keras-bert and the module can be called by R through reticulate package, which enables interoperability between Python and R.
